Supplementary Materials: The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-07-12 analysis/analysis.Rmd
best i can do

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_eeg_rms.pdf", width = 5.5, height = 8)
```

>>>>

both_plts <- p1 + p2 +  plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')
both_plts
ggsave("plots/subgroup_comp_eeg_rms.pdf", width = 5.5, height = 8)
```
